Low Complexity Adaptive Sonar Imaging

### 2016-03-01 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2016:03:01	20:09:13	(ti. 1.mars)

% \newcommand\mediaPath{gfx/media}
\newcommand\mediaPath{http://folk.uio.no/joibu/media/2015_JOE_LCA}

\newcommand\mediaI{\multimedia{\mediaPath/media1.mp4}{Media Movie~1}}
\newcommand\mediaII{\multimedia{\mediaPath/media2.mp4}{Media Movie~2}}

@@

Since LCA operates with the same optimization criterion as MVDR, we will be using approximately a factor 8 lateral oversampling for both beamformers. The images appear more visually pleasing and detailed up to 8. We consider an absolute minimum to be 2, due to the non-linear nature of delaying pixels that isn't strictly in the far field, and of displaying the absolute value of the pixels on a decibel scale. In \mediaI{} we visualize the effect of changing the lateral oversampling factor on a set of LCA images. Upon display the images are all bilinearly upinterpolated to the same size. 
% 
% \todo{Need $M$ in the image sector. Why???}

@@

\mediaII{} animates how \Fig{mvdr_selected_windows} changes as a function of the MVDR subarray length $L$ and temporal averaging $K$. At $L=1$ the window responses are rectangular in all areas in the image. At $L=2$ we observe window responses with slight amplitude variations in the highlight region, but with the phase being 0$^\circ$ in the illuminated seafloor sector. Already at $L=2$ the MVDR is able to greatly suppress noise. This is a common observation; adding a little flexibility to adapt to the scene has a dramatic effect, but further allowing full flexibility is much less significant. The media file also shows that MVDR can be run with subarray sizes $L\in[M/2,5M/8]$, but only with temporal averaging $K=1$ or above.

@@

@@

>>>>

% \newcommand\mediaPath{gfx/media}
\newcommand\articlePath{http://folk.uio.no/joibu/articles/2015_JOE_LCA}

\newcommand\mediaI{\multimedia{\articlePath/media1.mp4}{Media Movie~1}}
\newcommand\mediaII{\multimedia{\articlePath/media2.mp4}{Media Movie~2}}

@@

Since LCA operates with the same optimization criterion as MVDR, we will be using approximately a factor 8 lateral oversampling for both beamformers. The images appear more visually pleasing and detailed up to 8. We consider an absolute minimum to be 2, due to the non-linear nature of delaying pixels that isn't strictly in the far field, and of displaying the absolute value of the pixels on a decibel scale. In \mediaI{}\footnote{For media location refer to Appendix \ref{source_code}.} we visualize the effect of changing the lateral oversampling factor on a set of LCA images. Upon display the images are all bilinearly upinterpolated to the same size. 
% 
% \todo{Need $M$ in the image sector. Why???}

@@

\mediaII{}\footnote{For media location refer to Appendix \ref{source_code}.} animates how \Fig{mvdr_selected_windows} changes as a function of the MVDR subarray length $L$ and temporal averaging $K$. At $L=1$ the window responses are rectangular in all areas in the image. At $L=2$ we observe window responses with slight amplitude variations in the highlight region, but with the phase being 0$^\circ$ in the illuminated seafloor sector. Already at $L=2$ the MVDR is able to greatly suppress noise. This is a common observation; adding a little flexibility to adapt to the scene has a dramatic effect, but further allowing full flexibility is much less significant. The media file also shows that MVDR can be run with subarray sizes $L\in[M/2,5M/8]$, but only with temporal averaging $K=1$ or above.

@@

% \section{Steering angle}

\begin{figure}[t]%\centering%
\includegraphics[width=\linewidth]{gfx/buske8_online.eps}%
\caption{\emph{Steering angle needed to cut the -3\,dB distance of the Kaiser window's spatial response in half}. The needed amount of steering depends on the number of channels $M$, the element spacing relative to the wavelength $\frac{d}{\lambda}$, and the Kaiser parameter $\beta$. }\label{steering_angle_3dB}
\end{figure}
%
One of the goals of this article was to characterize the windows used by the MVDR method, and then identify a subset of these that were suitable for use with the LCA method. We determined that the Kaiser function could fit the role of producing the relevant windows. The spatial response of a steered Kaiser window depends on the number of channels $M$, the element spacing relative to the wavelength $\frac{d}{\lambda}$, the Kaiser parameter $\beta$, and the amount of steering $\phi$.

To control the resolution gain of LCA, we wanted to determine the extent that the windows need to be steered to cut the angle of the -3\,dB point of the window's spatial amplitude response by a fixed amount, say, by a factor 2 as reference. We computed this steering angle for some common configurations of the mentioned parameters. Refer to \Fig{steering_angle_3dB} for the result. The boundary values of the Kaiser window is shown, i.e. the rectangular window at $\beta=0$ and the near gaussian window at $\beta=5$, as well as one in between at $\beta=2.5$. Observe that for a given $M$ and $\beta$, the angle $\phi_\mathrm{3dB}$ scales near proportionally with $\frac{d}{\lambda}$. We found this to be true also for $\frac{d}{\lambda}\in\{0.5,4\}$. Hence, an approximate figure for a rather wide range of system parameters can be derived off this figure.

For the sake of completeness we also supply the source code, see Appendix \ref{source_code}.

@@

% \section{Multimedia Files and Source Code}\label{source_code}

This article is accompanied by some multimedia files and source code for determining the steering angles for LCA's windows. It is located at:

\url{\articlePath}
